Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
addressed another comment

Unfortunately, the CO maps at $6.1'$ are rather noisy,
and the vast majority of the sky has completely negligible CO emission. Thus,
in order to avoid adding unnecessary noise outside of molecular cloud complexes
and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$
 km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
resolution. This cut results in 90\% of the sky being unaffected by the CO 
correction, particularly the vast majority of the high Galactic latitude sky.

@@

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level
by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
absolute zero level tied largely to the reliable FIRAS zero point, and to some 
lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
Specifically, we fit a linear model to the FDS99 predicted 857 GHz values as a 
function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
zodiacal light and point sources removed and smoothed to 1$^{\circ}$ 
resolution, which we will refer to as $\mathcal{I}_{857}$. For this analysis, 
we considered $\mathcal{I}_{857}$ to be the independent variable, as it has 
much higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
prediction, as we have incorporated the finite bandpass correction factors 
described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
degree resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

>>>>

Unfortunately, the CO maps at $6.1'$ are rather noisy,
and the vast majority of the sky has completely negligible CO emission. Thus,
in order to avoid adding unnecessary noise outside of molecular cloud complexes
and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$
 km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
FWHM. This cut results in 90\% of the sky being unaffected by the CO 
correction, particularly the vast majority of the high Galactic latitude sky.

@@

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level
by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
absolute zero level tied largely to the reliable FIRAS zero point, and to some 
lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
Specifically, we fit a linear model to the FDS99 predicted 857 GHz values as a 
function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
zodiacal light and point sources removed and smoothed to 1$^{\circ}$ FWHM, 
which we will refer to as $\mathcal{I}_{857}$. For this analysis, we considered
$\mathcal{I}_{857}$ to be the independent variable, as it has much higher S/N 
than the FDS99 prediction, henceforward referred to as $\mathcal{F}_{857}$. 
Note that $\mathcal{F}_{857}$ is not a monochromatic prediction, as we have 
incorporated the finite bandpass correction factors described in 
$\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.
